% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Experiences}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
 \experience
    {Sept 15 2025}     {Senior R\&D Engineer}{Conflux}{\href{https://confluxnetwork.org}{\underline{confluxnetwork.org}}}
    {TILL NOW}    {
        \begin{itemize}
            \item Transparent Uniswap V3 liquidity NFT staking \& market making in single transaction.
            \item Demo of transparent trustless cross-chain transaction execution between Conflux eSpace and Aptos, with modified consensus codes and a custom type of transaction in Aptos.
            \item Massive performance test of Conflux-Rust, with multi-cloud servers around the globe.
            \item Documents for an asset cross-chain service of Conflux.
            \item Automatic tipping of 0.1 CFX for new asset holders via cross-chain.
        \end{itemize}
                    }
                    {Solidity, Rust, Move, Python, AWS, Alibaba Cloud, Tencent Cloud, vibe coding}
 \emptySeparator
 \experience
    {May 10 2021}     {Blockchain developer}{Smart Contracts, Infrastructures \& Security Audits}{\href{https://neo.org}{\underline{neo.org}}}
    {Feb 28 2025}    {
                      \begin{itemize}
                        \item Revolutionized testing \& debugging tools for Neo blockchain: \href{https://github.com/Hecate2/neo-fairy-test/}{\underline{Fairy}}\, (chain node plug-in for RPC-based testing \& debugging) with an automated \href{https://github.com/Hecate2/neo-fairy-client/}{\underline{client}}. Similar to but more powerful than \href{https://github.com/NomicFoundation/hardhat}{\underline{hardhat}}\, \& \href{https://github.com/trufflesuite/truffle}{\underline{truffle}}.
                        \item \href{https://github.com/neo-project/neo-devpack-dotnet/tree/master/src/Neo.Compiler.CSharp/Optimizer}{\underline{Neo smart contract assembly analyzer, optimizer}}, and \href{https://github.com/neo-project/neo-devpack-dotnet/tree/master/src/Neo.Compiler.CSharp/SecurityAnalyzer}{\underline{vulnerability scanner}}, supporting a mixture of try-catch-finally and ordinary control flow.
                        \item Researches on LLM, RAG and agent frameworks like LangGraph, Dify, ChromaDB and MongoDB. Preliminary construction for \href{https://github.com/xspoonai}{\underline{SpoonOS}}, a solution of MCP tools and LLM agents.
                        \item \href{https://github.com/Hecate2/RelationalDB}{\underline{Relational database implemented by smart contract and key-value database}}. Secondary index \& range query supported by splay tree.
                        \item Basic \href{https://github.com/Hecate2/oauth-account-backend}{\underline{backend}} in Rust for cryptographic operations of Neo account. Contributions of \href{https://github.com/r3e-network/NeoRust}{\underline{Neo implementation in Rust}}.
                        \item Miscellaneous docs \& \href{https://github.com/Hecate2/how-to-debug-neo/}{\underline{tutorials}} for debugging Neo blockchain at deepest source-code level.
                        \item \href{https://github.com/Hecate2/SukaLambda}{\underline{VM-like game skill engine}}, for arbitrary skill implementation. 
                        \item Miscellaneous DeFi \& DAO smart contracts:   \href{https://github.com/neoburger/}{\underline{NeoBurger}}, \href{https://github.com/Hecate2/neo-ruler/}{\underline{ruler protocol}}, \href{https://github.com/Hecate2/NFTLoan}{\underline{Divisible NFT}}\, standard \& loan, etc. Researched on MINLP algorithms to maximize profits, and \href{https://github.com/Hecate2/MerkleTreeForAirDrop}{\underline{zero-knowledge-proof airdrop contracts using Merkle tree}} to save GAS fees. 
                        \item Misc cryptography programs \& tutorials: \href{https://github.com/Hecate2/ECrecover}{\underline{Ethereum ECrecover instruction}} in C\# using Bouncy Castle; \href{https://github.com/Hecate2/RSA-xml-to-pem}{\underline{RSA keys from XML to PEM}}; \href{https://github.com/Hecate2/nep2wif}{\underline{Neo wallet to WIF format}}; \href{https://github.com/Hecate2/zk-principle}{\underline{zero-knowledge tutorial}}; helping design Ethereum-compatible anti-mev dBFT consensus protocol, using threshold encryption \& distributed key generation. 
                        \item Helped analyze Neo's VM, garbage collection, etc. , which lead to reveals of security vulnerabilities; Helped find VM instruction-level issues in Neo's smart contract compilers.
                        \item Misc Solidity contract tests using hardhat.
                        \item Performed on-chain data analysis; \href{https://github.com/Hecate2/eth_rpc_monitor/}{\underline{monitored}}\, some popular DeFi protocols on Ethereum.
                        \item Helped build a webpage-based functional demo utilizing Neo's features: NeoFS, digital ID system, oracle \& smart contracts. Analyzed the front end (using React) and smart contract codes. 
                      \end{itemize}
                    }
                    {Neo blockchain, smart contract, DeFi, neo-vm, compiler, tester, debugger, security audit, NeoFS, Solidity, hardhat, C\#, node.js, React, cryptography, consensus protocol, zero knowledge proof, MCP, LangGraph}
  \emptySeparator
 \experience
    {Mar 03 2025}     {Senior Smart Contract Engineer}{mETH Ethereum Staking Infrastructure}{\href{https://github.com/mantle-lsp}{\underline{github.com/mantle-lsp}}}
    {Aug 13 2025}    {
        \begin{itemize}
            \item mETH backend service maintenance: A41, blockdaemon, Kraken, P2P, Stakefish; SSV validators; oracles; Pectra upgrade.
            \item mETH contract security: blocking transfers of sanctioned accounts; reviews of bug bounty reports.
            \item Simulation infrastructures of Ethereum validator depositing, attesting and exiting, on private or public networks, with fully automatic signature service.
            \item Optimization of Ethereum validator exit sweep delay timing.
            \item Researches on \href{https://github.com/ethpandaops/ethereum-package}{\underline{ethereum-package}}, Omnichain Fungible Token (OFT) and Lido v3.
        \end{itemize}
                    }
                    {Solidity, foundry, golang, Ethereum staking, mETH}
  \emptySeparator
  \experience
    {June 2019} {\href{https://github.com/Hecate2/Ignareo-ISML-auto-voter}{\underline{Ignareo}}}{\href{https://github.com/Hecate2/Ignareo-ISML-auto-voter}{HTTP Spider Core of Ultimate Concurrency}}{150+ stars}
    {}    {
                      \begin{itemize}
                        \item Spiders packed in asynchronous tornado servers
                        \item Distributed broker architecture: aspects packaged as micro--service nodes
                        \item Covering shortages of scrapy: non-blocking sleep, user codes of better cohesion, freedom and tidiness; scalability with customized load--balancing
                        \item Seamless compatibility with anything based on asyncio or gevent
                        \item Combat-proven performance and stability
                      \end{itemize}
                    }
                    {distributed, web spider, asyncio, aiohttp, gevent, requests, tornado}
  \emptySeparator
   \experience
    {February 2020} {Intern backend developer}{Federated Learning Backend with Data Privacy}{\href{https://www.points.org}{\underline{www.points.org}}}
    {June 2020}    {
    A web service for cross--organization federated machine learning. Based on distributed datasets from different organizations, the training process should still keep strict data privacy of each data owner. The service is principally based on gRPC instead of HTTP.
                      \begin{itemize}
                        \item Basic but complete experience of commercial development flow: designing, coding, deploying, testing, pull request and code review. 111052++, 86888-- lines of code commits in the main repository.
                        \item Designed and wrote a user and API authorization backend. Wrote a data-usage approval backend.
                        \item Referring to horizontal learning APIs, developed vertical learning APIs. These APIs mostly involve data manipulation, but do not include core encryption and secret--sharing algorithms for learning. 
                        \item Wrote a basic service to retrieve real-time logs from docker containers and feed them to the frontend.
                        \item Developed basic automatic cross-system process tests for the APIs described above.
                        \item Implemented a mechanism to stop distributed vertical or horizontal training.
                        \item Built a basic client for on-line model inference service stress test, using \href{https://github.com/Hecate2/Ignareo-ISML-auto-voter}{\underline{Ignareo}}.
                        \item Tentatively designed a RESTful service for data providers to manage data, using flask and swagger.
                        \item Participated in software copyright registration and federated learning product standards.
                        \item Wrote docs and user manuals.
                      \end{itemize}
                    }
                    {protobuf, gRPC, sqlalchemy, redis (message queue), tensorflow-federated, dockerfile, docker-compose, git, Flask, swagger, Go}
  \emptySeparator
  \experience
    {August 2021}     {Intern backend developer}{Web Spider \& Flask Backend for OpenMMLab Operation Service}{\href{https://www.sensetime.com/}{\underline{SenseTime}} × \href{https://www.shlab.org.cn/}{\underline{Shanghai AI Lab}}}
    {September 2021}    {
                      \begin{itemize}
                        \item Maintained a system to fetch information from OpenMMLab's Github repositories and display info on a web page; send weekly e-mail reports based on fetched Feishu docs. Fixed miscellaneous bugs and implemented back end features.
                        \item Designed a process to migrate data from SQLite to MySQL (using DataGrip). 
                        \item Designed code for runtime multi-thread operations in Flask. 
                      \end{itemize}
                    }
                    {DataGrip, docker-compose, Flask, SQLAlchemy, apscheduler, requests}
  \emptySeparator
  \experience
    {July 2019}     {Intern developer}{High Concurrency Web Spider for Monitoring}{Johnson Controls}
    {August 2019}    {
                      \begin{itemize}
                        \item Monitored tens of thousands of IoT devices with help of \href{https://github.com/Hecate2/Ignareo-ISML-auto-voter}{\underline{Ignareo}}. 
                        \item Analyzed anomaly and output results to Excel sheets.
                        \item Provided a web service to browse and download the Excel files.
                      \end{itemize}
                    }
                    {Ignareo, requests, tornado, xlwings}
  \emptySeparator

\end{experiences}
